Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-06-14 writing/DraftExposurePaper/DraftExposurePaper.Rmd
Hurricane tracks now available in R
Kruk reference

#### Examples of using TS exposure estimates for multiple storms

@@

>>>>

Currently, it seems that most hurricane track mapping capabilities are restricted to geographical information system software. The introduction of this package expands the mapping potential of hurricane tracks and therefore the assessment of hurricane exposure and impacts to R.
#### Examples of using TS exposure estimates for multiple storms

@@

A recent study suggests that nearly all states east of the Rocky Mountains have experienced wind exposure associated with either tropical or post-tropical storms [@Kruk2010].
